Thermal tuning of phase-matching in a multimodal SOI waveguide with $\chi^{(3)}$ non linearity

### 2015-09-25 latex_raster/davide_bazzanella.tex
Errata corrige e presentazione

For our purpose, due to the thin geometry of the core, the waveguide does not support modes with the higher order in the height axis than the fundamental one.
The first row is of our interest.
Only one significant index is then left to describe the order of modes.
Figures (\ref{fig_ex_mode_TE}) and (\ref{fig_ex_mode_TM}) portray simulations of TE and TM third order modes.
\begin{figure}[!hb]
	\centering
	\includegraphics[width=0.89\textwidth]{output_modeTE.pdf}
	\caption{Example of third order TE mode in a \SI{3}{\um} wide waveguide [V/m]}
	\label{fig_ex_mode_TE}
\end{figure}
\begin{figure}[!h]
	\centering
	\includegraphics[width=0.89\textwidth]{output_modeTM.pdf}
	\caption{Example of third order TM mode in a \SI{3}{\um} wide waveguide [V/m]}
	\label{fig_ex_mode_TM}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=1\textwidth]{geometry.pdf}
	\label{fig_wg_Section}
	\caption{Section of the rectangular waveguide}
\end{figure}

@@

We positioned a thermal reservoir, a ``\textit{heater}", \SI{0.3}{\um} wide at the top of the cladding, exactly over the center of the waveguide core and set to mantain a specific temperature $T_H$ in the gap $[\SI{293.15}{\K} - \SI{693.15}{\K}]$, given by the configuration chosen.
To solve the heat equation we defined the density $\rho$ in [\si{\kg\m^3}], the thermal conductivity $\kappa_{TH}$ in [\si{\W\per\m\per\K}] and the heat capacity $C_P$ in [\si{\J\per\kg\per\K}] of the different materials.

\begin{table}[ht]
\centering
  \begin{tabular}{lcccc}  
    \toprule
		& \multicolumn{3}{c}{Properties} \\
    \cmidrule(r){2-5}
    	\multirow{2}{*}{Materials}    & $\rho$ & $\kappa_{TH}$ & $C_P$ & TOC\\
  		& [\si{\kg/\m^3}] & [\si{\W\per(\m\K)}] & [\si{\J\per(\kg\K)}] & [\si{\per\K}] \\
    \midrule
    Silicon (Si)			& 2329	& 130	& 700	& \num{1.87e-4}\\
    Silica (SiO$_2$)		& 2203	& 1.38	& 703	& 0\\
    \bottomrule
  \end{tabular}
  \label{tab_materials}
  \caption{Thermal properties of silicon and silica glass. \cite{n_db} and \cite{toc}}
\end{table}

Moreover, in order to be influenced by the different temperatures, we had to add to the definition of refractive index of the silicon a term dependent on the temperature.
For our purpose this dependence can easily be considered linear:
\begin{equation}
n = n(\lambda)+\mathrm{TOC}\cdot (T(x,y)-T_{amb})
\end{equation}
where $\mathrm{TOC}|_{\mathrm{Si}} = \SI{1.87e-4}{\per\K}$ is called Termo-Optic Coefficient. The coefficient of silica glass is negligible and therefore was considered zero $\mathrm{TOC}|_{\mathrm{SiO}_2} \approx 0$.

@@

\begin{figure}[!hb]
	\centering
	\includegraphics[width=1\textwidth]{thermal.pdf}
	\caption{Contour graph of a stationary solution for $T_H = T_{amb} + \SI{400}{\K}$}
	\label{fig_ex_thermal}
\end{figure}

@@

The second Figure (\ref{fig_sym_ppc2}) shows us that the change in position is of a fraction of \si{\nm}.
This value should be compared to the bandwidth of the phase-match condition.
In order to be interesting, its order of magnitude should be the same as the order of the bandwidth.

\begin{figure}[!h]
	\centering
	\includegraphics[width=.85\textwidth]{ppc2.png}
	\caption{Change of peak position. The label of the x axis are to be read as pump-signal-idler combinations. In order there are TE combinations and TM combinations.}
	\label{fig_sym_ppc2} % ppc = bandwidth change
\end{figure}

@@

Moreover there was almost no change in bandwidth as the temperature arised.
\begin{figure}[!h]
	\centering
	\includegraphics[width=.85\textwidth]{baat2.png}
	\caption{Bandwidth at $T_{amb}$. The label of the x axis are to be read as pump-signal-idler combinations. In order there are TE combinations and TM combinations.}
	\label{fig_sym_b@t2} % b@t = bandwidth @ T_amb
\end{figure}

@@

The new geometry is represented in Figure (\ref{fig_geometry_asym}).
\begin{figure}[!ht]
	\centering
	\includegraphics[width=.9\textwidth]{geometryA.pdf}
	\caption{Scheme of the side heater configuration.}
	\label{fig_geometry_asym}
\end{figure}

@@

\begin{figure}[!ht]
	\centering
	\includegraphics[width=.75\textwidth]{variation.png}
	\caption{Percentage variation of $n_{eff}$ for TE modes at \SI{1.55}{\um} from its value at ambient temperature in the symmetric configuration.}
	\label{fig_variation}
\end{figure}

@@

In Figure (\ref{fig_variation}) is represented the change of effective index, for wavelength $\lambda = \SI{1.55}{\um}$, from ambient temperature to \SI{400}{\K} over it in ratio to its value at $T_{amb}=\SI{293.15}{\K}$.
This curve suggest us that low orders are more influenced by the difference in temperature than high orders.
We can therefore hypothesize that configuration with a high difference between their orders could be controlled better.
In this view, as next step in enhancing the influence of temperature on effective index, different core geometries should be studied.
%, in order to maximise the effect of the overlap integrals between the optical mode and the thermal profile.
This could greatly condition the wave propagation, and therefore the thermal tuning, but it is also a difficult problem with many degrees of freedom.

>>>>

For our purpose, due to the thin geometry of the core, the waveguide does not support modes with the higher order in the height axis than the fundamental one.
The first row is of our interest.
Only one significant index is then left to describe the order of modes.
Figures (\ref{fig_ex_mode_TE}) and (\ref{fig_ex_mode_TM}) portray simulations of TE and TM third order modes.
\begin{figure}[!hb]
	\centering
	\includegraphics[width=0.89\textwidth]{output_modeTE.png}
	\caption{Example of third order TE mode in a \SI{3}{\um} wide waveguide [V/m]}
	\label{fig_ex_mode_TE}
\end{figure}
\begin{figure}[!h]
	\centering
	\includegraphics[width=0.89\textwidth]{output_modeTM.png}
	\caption{Example of third order TM mode in a \SI{3}{\um} wide waveguide [V/m]}
	\label{fig_ex_mode_TM}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=1\textwidth]{geometry.png}
	\label{fig_wg_Section}
	\caption{Section of the rectangular waveguide}
\end{figure}

@@

We positioned a thermal reservoir, a ``\textit{heater}", \SI{0.3}{\um} wide at the top of the cladding, exactly over the center of the waveguide core and set to mantain a specific temperature $T_H$ in the gap $[\SI{293.15}{\K} - \SI{693.15}{\K}]$, given by the configuration chosen.
To solve the heat equation we defined the density $\rho$ in [\si{\kg\per\m^3}], the thermal conductivity $\kappa_{TH}$ in [\si{\W\per(\m\K)}] and the heat capacity $C_P$ in [\si{\J\per(\kg\K)}] of the different materials.

\begin{table}[ht]
\centering
  \begin{tabular}{lcccc}  
    \toprule
		& \multicolumn{3}{c}{Properties} \\
    \cmidrule(r){2-5}
    	\multirow{2}{*}{Materials}    & $\rho$ & $\kappa_{TH}$ & $C_P$ & TOC\\
  		& [\si{\kg/\m^3}] & [\si{\W\per(\m\K)}] & [\si{\J\per(\kg\K)}] & [\si{\per\K}] \\
    \midrule
    Silicon (Si)			& 2329	& 130	& 700	& \num{1.87e-4}\\
    Silica (SiO$_2$)		& 2203	& 1.38	& 703	& 0\\
    \bottomrule
  \end{tabular}
  \label{tab_materials}
  \caption{Thermal properties of silicon and silica glass. \cite{toc} and \cite{n_db}}
\end{table}

Moreover, in order to be influenced by the different temperatures, we had to add to the definition of refractive index of the silicon a term dependent on the temperature.
For our purpose this dependence can easily be considered linear:
\begin{equation}
n = n(\lambda)+\mathrm{TOC}\cdot (T(x,y)-T_{amb})
\end{equation}
where $\mathrm{TOC}|_{\mathrm{Si}} = \SI{1.87e-4}{\per\K}$ is called Thermo-Optic Coefficient. The coefficient of silica glass is negligible and therefore was considered zero $\mathrm{TOC}|_{\mathrm{SiO}_2} \approx 0$.

@@

\begin{figure}[!hb]
	\centering
	\includegraphics[width=1\textwidth]{thermal.png}
	\caption{Contour graph of a stationary solution for $T_H = T_{amb} + \SI{400}{\K}$}
	\label{fig_ex_thermal}
\end{figure}

@@

The second Figure (\ref{fig_sym_ppc2}) shows us that the change in position is of a fraction of \si{\nm}.
This value should be compared to the bandwidth of the phase-match condition.
In order to be interesting, its order of magnitude should be the same as the order of the bandwidth, or at most one order of magnitude less than the bandwith.

\begin{figure}[ht]
	\centering
	\includegraphics[width=.85\textwidth]{ppc2.png}
	\caption{Change of peak position. The label of the x axis are to be read as pump-signal-idler combinations. In order there are TE combinations and TM combinations.}
	\label{fig_sym_ppc2} % ppc = bandwidth change
\end{figure}

@@

Moreover there was almost no change in bandwidth as the temperature arised.
\begin{figure}[hb]
	\centering
	\includegraphics[width=.85\textwidth]{baat2.png}
	\caption{Bandwidth at $T_{amb}$. The label of the x axis are to be read as pump-signal-idler combinations. In order there are TE combinations and TM combinations.}
	\label{fig_sym_b@t2} % b@t = bandwidth @ T_amb
\end{figure}

@@

The new geometry is represented in Figure (\ref{fig_geometry_asym}).
\begin{figure}[!ht]
	\centering
	\includegraphics[width=.9\textwidth]{geometryA.png}
	\caption{Scheme of the side heater configuration.}
	\label{fig_geometry_asym}
\end{figure}

@@

\begin{figure}[!ht]
	\centering
	\includegraphics[width=.75\textwidth]{TOEvariation.png}
	\caption{Effective TOE for TE modes at \SI{1.55}{\um}.}
	\label{fig_variation}
\end{figure}

@@

In Figure (\ref{fig_variation}) is represented the effective TOE of different modes, for wavelength $\lambda = \SI{1.55}{\um}$.
This curve suggest us that high orders are more influenced by the difference in temperature than low orders.
We can therefore hypothesize that configuration with a high difference between their orders could be controlled better.
In this view, as next step in enhancing the influence of temperature on effective index, different core geometries should be studied.
%, in order to maximise the effect of the overlap integrals between the optical mode and the thermal profile.
This could greatly condition the wave propagation, and therefore the thermal tuning, but it is also a difficult problem with many degrees of freedom.

### 2015-09-25 presentazione/presentazione.tex
Errata corrige e presentazione

\documentclass[11pt]{beamer}
%\usetheme{Montpellier}
\usetheme{Dresden}
\usepackage[utf8]{inputenc}
\usepackage[italian]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[compatibility=false]{caption}
\usepackage{subcaption}
\usepackage{multicol}
\author{Davide Bazzanella}
\title{Thermal tuning of phase-matching in a multimodal SOI waveguide with $\chi^{(3)}$ non linearity}
\date{28 settembre 2015} 
%\textsc{\LARGE \textbf{DEPARTMENT OF PHYSICS}}\\[0.5cm]
%\textsc{\LARGE \textbf{DEGREE IN PHYSICS – LAUREA IN FISICA}}\\[2.5cm]
%\textsc{\Large THESIS}\\[1.3cm]

@@

\begin{frame}{Outline}
\footnotesize \tableofcontents
\end{frame}

\section{Introduction}
ciao
\section{Nonlinear Optics}
\subsection{Four-Wave Mixing}
\subsection{Conservation of energy and momentum}
\subsubsection{Multimodal Waveguides}
\subsection{Peak tuning}
\subsubsection{Thermo-Optic Coefficient}
\section{Computational model}
\subsection{Mode simulation}
\subsection{•}
\subsection{Results}
\section{Conclusion}

\end{document}

>>>>

\documentclass[11pt, leqno]{beamer}
%\usetheme{Montpellier}
\usetheme{Dresden}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[compatibility=false]{caption}
\usepackage{subcaption}
\usepackage{multicol}

\usepackage{siunitx}
\usepackage{wrapfig}
%\usepackage{float}

\usepackage{caption}
\usepackage{subcaption}

\author{Davide Bazzanella}
\title{Thermal tuning of phase-matching in a multimodal SOI waveguide with $\chi^{(3)}$ non linearity}
\date{28 settembre 2015} 
%\textsc{\LARGE \textbf{DEPARTMENT OF PHYSICS}}\\[0.5cm]
%\textsc{\LARGE \textbf{DEGREE IN PHYSICS – LAUREA IN FISICA}}\\[2.5cm]
%\textsc{\Large THESIS}\\[1.3cm]

@@

\begin{frame}{Outline}
%\footnotesize
\tableofcontents
\end{frame}

\section{Introduction}
\begin{frame}{Introduction}

	\textbf{Research field}:\\
	bio-sensors, gas sensors and bio-medical instrumentation

	\vspace{5pt}
	\textbf{Problem}:\\
	lack of sources/sensors in the MIR (3-10\si{\um})

	\begin{figure}
		\centering
		\includegraphics[width=\textwidth]{spectrum2.png}
	\end{figure}
\end{frame}
\begin{frame}
	\textbf{Solution}:\\
	frequency down convertion from NIR/VIS sources to MIR\\
	frequency up convertion from MIR signals to NIR/VIS sensor

	\begin{figure}[hb]
%		\centering
%		\begin{subfigure}[c]{.725\textwidth}
			\centering
			\includegraphics[width=.75\textwidth]{upconversion2_short.png}
%			\caption{}
%		\end{subfigure}
%		\hspace{0.02\textwidth}
%		\begin{subfigure}[c]{.225\textwidth}
%			\centering
%			\includegraphics[width=\textwidth]{upconverter_HITACHI.png}
%			\caption{}
%		\end{subfigure}
	\end{figure}	
%	\vspace{15pt}
	\textbf{Aim}:\\
	Develop integrated frequency converter tunable with temperature
\end{frame}

\section{Nonlinear Optics}
\begin{frame}{Nonlinear Optics}
	Frequency convertion employs nonlinear properties of materials
	\begin{equation}
		\textbf{P} = \varepsilon_0 \left( \chi^{(1)} \cdot \textbf{E} + \chi^{(2)} : \textbf{E}^2 + \chi^{(3)} \vdots \textbf{E}^3 + \cdots \right) = \mathrm{\textbf{P}_L} + \mathrm{\textbf{P}_{NL}}
		\label{eq_P_general}
	\end{equation}
	\begin{wrapfigure}{r}{0.33\textwidth}
		\centering
		\includegraphics[width=.3\textwidth]{upconverter_HITACHI.png}
	\end{wrapfigure}
	\begin{itemize}
	\item	$\chi^{(1)}$	:	linear part
	\item	$\chi^{(2)}$	:	2$^{nd}$ order nonlinearity\\ \hspace{25pt} (SHG, TWM)
	\item	$\chi^{(3)}$	:	3$^{rd}$ order nonlinearity\\ \hspace{25pt} (THG, FWM)
	\end{itemize}
\end{frame}
%\subsection{Four-Wave Mixing}
\begin{frame}{Four-Wave Mixing}
	%\begin{wrapfigure}{r}{0.22\textwidth}
	%    \includegraphics[width=.22\textwidth]{photons.png}
	%\end{wrapfigure}
	\begin{wrapfigure}{r}{0.35\textwidth}
		\vspace{-20pt}
	    \includegraphics[width=.33\textwidth]{W&K.png}
	\end{wrapfigure}
	FWM uses 3$^{rd}$ order nonlinearity $\chi^{(3)}$.
	%\begin{wrapfigure}{r}{0.22\textwidth}
	%    \includegraphics[width=.22\textwidth]{momentum.png}
	%\end{wrapfigure}

	\vspace{10pt}
	It consists of the interaction between four EM waves of different frequencies.
	\begin{align}
	\omega_1 + \omega_2 &= \omega_3 + \omega_4\\
	k_1 + k_2 &= k_3 + k_4
	\label{eq_general_f}
	\end{align}

	\vspace{5pt}
	Special case:\\ $\omega_1 = \omega_2 = \omega_P$, with stimulation.
\end{frame}
%\subsection{Conservation of energy and momentum}
\begin{frame}{Conservation of energy and momentum}
	\begin{figure}
		\centering
		\vspace{10pt}
		\includegraphics[width=.8\textwidth]{setup_b&w.png}
	\end{figure}
	Conservation of energy is naturally verified
	\begin{equation}
		\omega_I = 2\omega_P - \omega_S = \omega_P \pm \Omega
		\label{eq_energy}
	\end{equation}
	Conservation of momentum is imposed on the phase-mismatch
	\begin{equation}
		\Delta k = 2\,k_P(\omega_P) - k_S(\omega_S) -k_I(\omega_I) = 0
		\label{eq_momentum}
	\end{equation}
	%\begin{equation*}
	%\mathrm{where} \qquad k = \frac{\omega}{c} = \frac{2\pi}{\lambda}
	%\end{equation*}
\end{frame}
\begin{frame}
	Generation happens also for $\Delta k \approx 0$, but at lower efficiency.
	\begin{wrapfigure}{r}{0.5\textwidth}
		\vspace{10pt}
		\centering
	    \includegraphics[width=.5\textwidth]{sinc2.png}
	\end{wrapfigure}
	\begin{equation}
	\begin{split}
		I_I &\propto \left| \int_0^L exp(\mathrm{i}\Delta k z)dz\right| \\
			&\propto L^2 sinc(\Delta k / 2\pi)
	\end{split}
	\end{equation}
	We define the coherence length
	\begin{equation}
		L_{coh} = \frac{2\pi}{|\Delta k|}
	\label{eq_coherence_length}
	\end{equation}
\end{frame}
\begin{frame}
	Bulk silicon does not permit to verify both equations.
	\begin{equation}
	k(\omega) = k_0 n(\omega)
	\label{eq_k(w)}
	\end{equation}
	\begin{figure}
		\centering
%		\vspace{-5pt}
		\includegraphics[width=0.8\textwidth]{RefractiveIndexINFO.pdf}
		\label{fig_silicon_dispersion}
	\end{figure}
\end{frame}
%\subsubsection{Multimodal Waveguides}
\begin{frame}{Multimodal Waveguides}
	In silicon waveguides both equations can be verified.\\
	Therefore Eq. \eqref{eq_momentum} becomes:
	\begin{equation}
		\Delta k = 2\,\beta_P(\omega_P) -\beta_S(\omega_S) -\beta_I(\omega_I)
		\label{eq_beta}
	\end{equation}
	\begin{equation*}
		\mathrm{where} \qquad	\beta(\omega) = k_0 n_{eff}(\omega)
	\end{equation*}
	\vspace{-5pt}
	\begin{itemize}
	\item	If the waveguide supports only one mode, phase-matching is only near the frequency of the pump and $\Omega \ll \omega_P$
	\item	If the waveguide is multimodal, there are more matching conditions and also $\Omega \lesssim \omega_P$.
	\end{itemize}
\end{frame}

%\subsection{Phase-matching tuning}
\begin{frame}{Phase-matching tuning}
	\begin{wrapfigure}{r}{0.5\textwidth}
		\vspace{-10pt}
		\centering
	    \includegraphics[width=.55\textwidth]{narrow_bandwidth.png}
	\end{wrapfigure}
	Phase-matching conditions have narrow bandwidth.

	\vspace{20pt}
	It is difficult to obtain phase-matching at the required wavelength.

	\vspace{20pt}
	We aim to tune with temperature the range where phase-matching is verified.
\end{frame}
%\subsubsection{Thermo-Optic Coefficient}
\begin{frame}{Thermo-Optic Coefficient}
	Refractive index of silicon is influenced from the temperature.

	\begin{equation}
	\begin{split}
		n 	&= n(\omega,T(x,y)) \\
			&= n(\omega,T_{amb}) + \mathrm{TOC}\cdot(T(x,y)-T_{amb})
		\label{eq_refractive_index}
	\end{split}
	\end{equation}

	\vspace{10pt}
	Different modes react differently at the change of temperature.
	\begin{equation}
		n_{eff} = n_{eff}(\omega,T_{amb}) + \mathrm{TOC}_{eff}\cdot(T_H-T_{amb})
		\label{eq_effective_index}
	\end{equation}
\end{frame}
\begin{frame}
	\begin{figure}
		\centering
		\vspace{-10pt}
		\includegraphics[width=.8\textwidth]{effectiveTOC.pdf}
		\label{fig_TOC_effective}
		\vspace{-10pt}
	\end{figure}
	It should be possible to control phase-matching with temperature.
\end{frame}
\section{Computational model}
\begin{frame}{Computational model}
	\begin{figure}
%		\vspace{-15pt}
		\centering
		\includegraphics[width=\textwidth]{geometry.pdf}
	\end{figure}
\end{frame}
%\subsection{Temperature simulation}
\begin{frame}{Temperature simulation}
	\begin{figure}
%		\vspace{-15pt}
		\centering
		\includegraphics[width=\textwidth]{thermal.pdf}
	\end{figure}
\end{frame}
%\subsection{Mode simulation}
\begin{frame}{Mode simulation}
	\begin{figure}
%		\vspace{-15pt}
		\centering
		\includegraphics[width=\textwidth]{output_modeTE.pdf}
	\end{figure}
\end{frame}
\begin{frame}{Mode simulation}
	\begin{figure}
%		\vspace{-15pt}
		\centering
		\includegraphics[width=\textwidth]{output_modeTM.pdf}
	\end{figure}
\end{frame}
\section{Data analysis}
\begin{frame}{Data analysis}
	\begin{itemize}
	\item	Data extraction from comsol to matlab.
	\item	Data classification (TE/TM, order).
	\item	Data processing:\\
			\begin{itemize}
			\item	polynomial fit of $\lambda$ and $T_H$.
			\item	evaluation of phase-mismatch \eqref{eq_momentum} with \eqref{eq_beta} and \eqref{eq_effective_index}
					\begin{equation}
					\Delta k = 2	 \frac{2\pi}{ \lambda_P } n_{eff}(\lambda_P,T_H)
								-\frac{2\pi}{ \lambda_S } n_{eff}(\lambda_S,T_H)
								-\frac{2\pi}{ \lambda_I } n_{eff}(\lambda_I,T_H)
					\end{equation}
					and coherence length $L_{coh} = \frac{2\pi}{|\Delta k|}$.
			\end{itemize}
	\item	Data selection: verify condition $L_{coh}/L_{sam} \geq 1$.
	\item	Data aggregation.
	\end{itemize}
\end{frame}
\section{Results}
\begin{frame}{Results: symmetric configuration}
	\begin{figure}
%		\vspace{-15pt}
		\centering
		\includegraphics[height=.8\textheight]{ppaat22.png}
	\end{figure}
\end{frame}
\begin{frame}
	\begin{figure}
%		\vspace{-15pt}
		\centering
		\includegraphics[height=.9\textheight]{baat2.png}
	\end{figure}
\end{frame}
\begin{frame}
	\begin{figure}
%		\vspace{-15pt}
		\centering
		\includegraphics[height=.9\textheight]{ppc2.png}
	\end{figure}
\end{frame}
\begin{frame}
	Combination \texttt{TE 517}, symmetric configuration.
	\begin{figure}
%		\vspace{-15pt}
		\centering
		\includegraphics[width=.8\textwidth]{bandwidth_movement_TE517_sym.png}
	\end{figure}
\end{frame}
\begin{frame}{Asymmetric configuration}
	\begin{figure}
%		\vspace{-15pt}
		\centering
		\includegraphics[width=\textwidth]{geometryA.pdf}
	\end{figure}
\end{frame}
\begin{frame}
	\begin{figure}
%		\vspace{-15pt}
		\centering
		\includegraphics[height=.85\textheight]{asym_ppc2.png}
	\end{figure}
\end{frame}
\section{Conclusion}
%\subsection{Improvements}
\begin{frame}{Improvements}
	\begin{itemize}
		\item	The heater should be simulated as a metal conductor media, instead of a simple boundary condition (TM modes).
		\item	Thermo-Optic Coefficient also depends on the wavelength of the signal.
		\item	Different core geometries should be studied.
		\item	Develop the correlation also between temperature and efficiency of energy conversion.
	\end{itemize}
\end{frame}
%\subsection{Summary}
\begin{frame}{Summary}
	\begin{itemize}
		\item Configurations with a high difference between their orders are to be preferred.
		\item Limited interaction between the temperature of material and different modes is a constraint.
		\item Thermal tuning of the FWM phase-match is, in fact, possible.
	\end{itemize}
\end{frame}
\end{document}
